On particular diameter bounds for integral point sets in higher dimensions \footnote{ This work was carried out at Voronezh State University and supported by Russian Science Foundation grant 19-11-00197. }

### 2021-11-06 AvdMomZvol_rails/Article.tex
[AMZr] Acknowledgements
[AMZr] Section refs - just in case

\section{Introduction}

@@

In this paper we further study the various features of IPS.
In Section 2, we discuss the classification of planar integral points sets;
in Sections 3 and 4, we present some bounds for $d(m,n)$ based on planar integral point sets of special types
and provide some general constructions of such bounds.

\section{Classification of planar integral point sets}

@@

\section{Bounds based on rails sets}

@@

\section{Bounds based on pyramid sets}

@@

>>>>

\section{Introduction}
\label{sec:intro}

@@

In this paper we further study the various features of IPS.
In Section~\ref{sec:classif}, we discuss the classification of planar integral points sets;
in Sections~\ref{sec:bounds_rails}~and~\ref{sec:bounds_pyramid}, we present some bounds for $d(m,n)$ based on planar integral point sets of special types
and provide some general constructions of such bounds.

\section{Classification of planar integral point sets}
\label{sec:classif}

@@

\section{Bounds based on rails sets}
\label{sec:bounds_rails}

@@

\section{Bounds based on pyramid sets}
\label{sec:bounds_pyramid}

@@

\section{Acknowledgements}
The author thanks Dr. A.S. Usachev for his help in polishing the text of the paper.
